An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-30 paper/paper.tex
Paper: lowercase "protocol" in abstract

\begin{abstract}
For many computer users, having access to a reliable file backup service is important. As computers and computer-related technologies improve, users have the ability to generate higher resolution content. Creating backups becomes less feasible as the amount of data grows; limited network bandwidth makes the backup process cumbersome, and access to a large amount of storage space for backups is either limited or expensive. In this report, we propose a new backup system, BTBackup, which aims to solve both problems. Our system is designed as a Peer-to-Peer (P2P) network, where users of the system use each other as backup locations. Users offer storage space that is proportional to the amount of data that they back up. This means that the capacity of each user's physical storage is the only limiting factor for how much they can back up. We solve the problem of long data transfers for big files by leveraging the speed offered by the BitTorrent Protocol, which uses a file chunking mechanism to download files from multiple peers at once. By testing our system in various scenarios, we show that it achieves our goal of quicker backup creation and recovery through the use of file transfer parallelization.
\end{abstract}

@@

A high-level overview of our system is offered in Figure \ref{fig:SystemDesign}. We explain each of these components in the following sections. In this figure, the components enclosed in rectangles are internal to our system, while the ones in ovals are external. Connections with arrowheads represent a unidirectional flow of information, while connections with no arrowheads represent a bidirectional flow of information.

>>>>

\begin{abstract}
For many computer users, having access to a reliable file backup service is important. As computers and computer-related technologies improve, users have the ability to generate higher resolution content. Creating backups becomes less feasible as the amount of data grows; limited network bandwidth makes the backup process cumbersome, and access to a large amount of storage space for backups is either limited or expensive. In this report, we propose a new backup system, BTBackup, which aims to solve both problems. Our system is designed as a Peer-to-Peer (P2P) network, where users of the system use each other as backup locations. Users offer storage space that is proportional to the amount of data that they back up. This means that the capacity of each user's physical storage is the only limiting factor for how much they can back up. We solve the problem of long data transfers for big files by leveraging the speed offered by the BitTorrent protocol, which uses a file chunking mechanism to download files from multiple peers at once. By testing our system in various scenarios, we show that it achieves our goal of quicker backup creation and recovery through the use of file transfer parallelization.
\end{abstract}

@@

A high-level overview of our system is offered in Figure \ref{fig:SystemDesign}. We explain each of these components in the following sections. In this figure, the components enclosed in rectangles are internal to our system, while the ones in ovals are external. Connections with arrowheads represent a unidirectional flow of information, while connections with no arrowheads represent a bidirectional flow of information. Components that are colored green are part of the system core.
